Visualising metagenome differences

### 2023-11-21 analysis/metagenome.Rmd
add consistent color scheme for orders

```{r}
colors <-c(microshades_palette("micro_blue", 4, lightest = FALSE), 
           microshades_palette("micro_purple", 4, lightest = FALSE),
           microshades_palette("micro_green", 4, lightest = FALSE),
           microshades_palette("micro_orange", 4, lightest = FALSE))

>>>>

```{r}
colors <-c(microshades_palette("micro_blue", 4, lightest = FALSE), 
           microshades_palette("micro_purple", 4, lightest = FALSE),
           microshades_palette("micro_green", 4, lightest = FALSE),
           microshades_palette("micro_orange", 4, lightest = FALSE))
names(colors) <- c("Rhizobiales", "Clostridiales", "Desulfobacterales", "Chitinophagales", 
"Chromatiales", "Solirubrobacterales", "Xanthomonadales", "Acidimicrobiales", 
"Rhodobacterales", "Corallinales", "Ceramiales", "Alismatales", 
"Thiotrichales", "Flavobacteriales", "Remainder", "Unclassified")
```
